Computable Poincar\'e--Friedrichs constants for the $L^{p}$ de~Rham complex over convex domains and domains with shellable triangulations

### 2025-02-03 main.tex
new table entries, completed, abbreviated
outlook

\begin{table}[t]
    \centering
    \begin{tabular}{|c||c|c|c|c|c||c|c|c|}
        \hline
                        & $\grad$ ref  & $\grad$ est & $\grad$ ratio & $\grad$ est & $\grad$ ratio      & $\divergence$ ref  & $\divergence$ est  & $\divergence$ ratio \\ 
        \hline
        $\calT_{Q}$     & 0.318        & 0.9040624834 &               & 0.904062477        & 3.141        & 0.225              & 1.339553527              &  6.928              \\
        \hline
        $\calT_{L}$     & 0.822        & 2.381225711 &               & 1.421249625        & 2.895              & 0.322              & 2.505543143         &  7.402              \\
        \hline
        $\calT_{L'}$     & 0.822        & 2.391924501 &               & 2.391924492        & 2.895              & 0.322              & 4.053039867        &  7.402              \\
        \hline
        $\calT_{S,5}$     & 0.978        & 2.752696283 &               & 1.779367097       & 2.982              & 0.346              & 3.717588832       &  8.419              \\ 
        \hline % centered
        $\calT_{S'}$    & 0.978        & 3.131764309 &               & 3.131764307       & 4.870              & 0.346              & 5.453759801         & 13.748              \\
        \hline % non-centered
        $\calT_{S''}$   & 0.978        & 2.761956509 &               & 2.761956506       & 4.870              & 0.346              & 4.662992222         & 13.748              \\
        \hline
    \end{tabular}
    \caption{
    Estimates for $L^2$ Poincar\'e--Friedrichs constants over various triangulated 2D domains.
    Reference values for the gradient and divergence (2nd and 7th column) computed with finite element methods together with estimates and ratios: 
    Theorem~\ref{theorem:poincarefriedrichsestimate:grad} (3rd and 4th column), using Theorem~\ref{theorem:poincarefriedrichsestimate:exterior} with $k=0$ (5th and 6th column), 
    and using Theorem~\ref{theorem:poincarefriedrichsestimate:exterior} with $k=0$ (8th and 9th column).
    Note that the divergence constant can always be estimated using Lemma~\ref{lemma:mixedbconsimplex}.
    }\label{table:estimates2D}
\end{table}

@@

We consider the following example domains in two dimensions:
the unit cube $\Omega_C$, the Fichera corner domain $\Omega_F$, and the crossed bricks domain $\Omega_{B}$:
\begin{gather*}
    \Omega_{C}  = ( 0,1)^3,
    \qquad 
    \Omega_{F}  = (-1,1)^3 \setminus [0,1)^3,
    \\
    \begin{aligned}
    \Omega_{B} &= 
    \left( (-1,0) \times (-1,0) \times (-1,1) \right)
    \\&\qquad
    \cup 
    \left( (-1,0) \times (-1,1) \times (-1,0) \right)
    \\&\qquad
    \cup 
    \left( (-1,1) \times (-1,0) \times (-1,0) \right)
    .
    \end{aligned}
\end{gather*}
We consider the triangulations: 
\begin{itemize}
    \item $\calT_{C}$: cube triangulation with five tetrahedra
    \item $\calT_{K}$: Kuhn triangulation of the cube, consisting of six tetrahedra
    \item $\calT_{F}$: Fichera corner, $24$ simplices 
    \item $\calT_{B}$: crossed bricks, $24$ simplices 
\end{itemize}

@@

\begin{table}[t]
    \color{red}
    \centering
    \begin{tabular}{|c|c|c|c|c|c|c|c|c|}
        \hline
                        & $\grad$ ref  & $\grad$ est  & $\grad$ ratio      & $\grad$ est & $\grad$ ratio       \\
        \hline
        $\calT_{C,5}$   & 0.3179254398 & 4.31776537   &                    & 3.246136642  & 91.66905966662563  \\
        \hline
        $\calT_{C,K}$   & 0.3041392027 & 0.3177997026 &                    & 11.03485346 & 3.611339490040196  \\
        \hline
        $\calT_{B,5}$   & 1.022627161  & 7.698889039  &                    & 25.97226447  & 35.96824737574127  \\
        \hline
        $\calT_{B,K}$   & 1.022627161  & 10.10602558  &                    & 53.76320901  & 61.02495966269372  \\
        \hline
        $\calT_{F}$     & 0.7117133306 &              &                    & 325.7340627  & 18796.92616132183  \\
        \hline
    \end{tabular} 
    \caption{
    Estimates for $L^2$ Poincar\'e--Friedrichs constants of the gradient over various triangulated 3D domains.
    Reference values for the gradient (2nd column) computed with finite element methods together with estimates and ratios: 
    Theorem~\ref{theorem:poincarefriedrichsestimate:grad} (3rd and 4th column), and using Theorem~\ref{theorem:poincarefriedrichsestimate:exterior} with $k=0$ (5th and 6th column).
    }\label{table:estimates3D:grad}
\end{table}

\begin{table}[t]
    \color{red}
    \centering
    \begin{tabular}{|c|c|c|c|c|c|c|c|c|}
        \hline
                        & $\curl$ ref  & $\curl$ est & $\curl$ ratio     & $\divergence$ ref & $\divergence$ est & $\divergence$ ratio \\ 
        \hline
        $\calT_{K,5}$   & 0.2250062929 & 141.1488115 & 129.5249378629681 & 0.1837655124      & 3.391164992       & 139.7449800105412   \\
        \hline
        $\calT_{C,K}$   & 0.2250695032 & 12.15727753 & 5.099236457042005 & 0.1837881324      & 25.89943821       &  8.30608900893      \\
        \hline
        $\calT_{B,5}$   & 0.3315710272 & 113.0845771 & 482.5669036190229 & 0.2330604743      & 152.8861269       &    \\
        \hline
        $\calT_{B,K}$   & 0.3315710272 & 162.6872182 & 1726.182004903473 & 0.2330604743      & 512.2731352       & 2191.733177984011   \\
        \hline
        $\calT_{F}$     & 0.5549678737 & 13378.02292 & 24105.94118711908 & 0.3106774562      & 11705.58269       & 37677.60567703448   \\ 
        \hline
    \end{tabular}
    \caption{
    Estimates for $L^2$ Poincar\'e--Friedrichs constants over various triangulated 3D domains.
    Reference values for the curl and divergence (2nd and 5th column) computed with finite element methods together with estimates and ratios
    that rely on Theorem~\ref{theorem:poincarefriedrichsestimate:exterior} with $k=0$ (3rd and 4th column) and with $k=1$ (5th and 6th column).
    Note that the divergence constant can always be estimated using Lemma~\ref{lemma:mixedbconsimplex}.
    }\label{table:estimates3D:curldiv}
\end{table}

@@

The most important contribution of this manuscript is the computation of upper bounds of Poincar\'e--Friedrichs constants for the curl and divergence operators over local patches in low dimensions (i.e., \ $n=2$ or $n=3$). 
However, our upper bounds are hardly the last word on estimating the Poincar\'e--Friedrichs constants over local patches (stars). There are several avenues for further research and improvement.

We use local Poincar\'e--Friedrichs inequalities over single simplices, subject to boundary conditions along some faces. As mentioned earlier, the Poincar\'e constant over triangles admits a sharper upper bound than for general convex domains. We conjecture that tetrahedra permit a similar improvement.

The gradient Poincar\'e--Friedrichs constant already dominates the Poincar\'e--Friedrichs constants of the $\Lebesgue^2$ de~Rham complex without boundary conditions (or with full boundary conditions) over convex domains~\cite{guerini2004eigenvalue,licht2024geometry}. 
We believe that this generalizes to the entire range of Lebesgue exponents $1 \leq p \leq \infty$
Such estimates would likely improve on the Poincar\'e--Friedrichs constants derived via the regularized Poincar\'e and Bogovski\u{\i} operators.

>>>>

\begin{table}[t]
    \centering
    \begin{tabular}{|r||r|r|r|r|r||r|r|r|}
        \hline
                        & $\grad$ ref  & $\grad$ est & $\grad$ ratio       & $\grad$ est   & $\grad$ ratio      & $\divergence$ ref  & $\divergence$ est  & $\divergence$ ratio \\ 
        \hline
        $\calT_{Q}$     & 0.318        & 0.904       & 2.842               & 0.904         & 2.842              & 0.225              & 1.339              &  5.953         \\
        \hline
        $\calT_{L}$     & 0.822        & 2.381       & 2.896               & 1.421         & 1.729              & 0.322              & 2.505              &  7.781         \\
        \hline
        $\calT_{L'}$    & 0.822        & 2.391       & 2.909               & 2.391         & 2.909              & 0.322              & 4.053              & 12.587         \\
        \hline
        $\calT_{S,5}$   & 0.978        & 2.752       & 2.814               & 1.779         & 1.819              & 0.346              & 3.717              & 10.744         \\ 
        \hline % centered
        $\calT_{S'}$    & 0.978        & 3.131       & 3.202               & 3.131         & 3.202              & 0.346              & 5.453              & 15.762         \\
        \hline % non-centered
        $\calT_{S''}$   & 0.978        & 2.761       & 2.824               & 2.761         & 2.824              & 0.346              & 4.662              & 13.476         \\
        \hline
    \end{tabular}
    \caption{
    Estimates for $L^2$ Poincar\'e--Friedrichs constants over various triangulated 2D domains.
    Reference values for the gradient and divergence (2nd and 7th column) computed with finite element methods together with estimates and ratios: 
    Theorem~\ref{theorem:poincarefriedrichsestimate:grad} (3rd and 4th column), using Theorem~\ref{theorem:poincarefriedrichsestimate:exterior} with $k=0$ (5th and 6th column), 
    and using Theorem~\ref{theorem:poincarefriedrichsestimate:exterior} with $k=0$ (8th and 9th column).
    Note that the divergence constant can always be estimated using Lemma~\ref{lemma:mixedbconsimplex}.
    }\label{table:estimates2D}
\end{table}

@@

We consider the following example domains in two dimensions:
the unit cube $\Omega_C$, the Fichera corner domain $\Omega_F$, and the crossed bricks domain $\Omega_{B}$:
\begin{gather*}
    \Omega_{C}  = ( 0,1)^3,
    \qquad 
    \Omega_{F}  = (-1,1)^3 \setminus [0,1)^3,
    \\
    \begin{aligned}
    \Omega_{B} &= 
    \left( (-1,0) \times (-1,0) \times (-1,1) \right)
    \\&\qquad
    \cup 
    \left( (-1,0) \times (-1,1) \times (-1,0) \right)
    \\&\qquad
    \cup 
    \left( (-1,1) \times (-1,0) \times (-1,0) \right)
    .
    \end{aligned}
\end{gather*}
We consider the triangulations: 
\begin{itemize}
    \item $\calT_{C,5}$: cube triangulation with five tetrahedra
    \item $\calT_{C,K}$: Kuhn triangulation of the cube, consisting of six tetrahedra
    \item $\calT_{B,5}$: crossed bricks, four copies of $\calT_{C,5}$
    \item $\calT_{B,K}$: crossed bricks, four copies of $\calT_{C,K}$
    \item $\calT_{F}$: Fichera corner, $24$ simplices 
\end{itemize}

@@

\begin{table}[t]
    \color{red}
    \centering
    \begin{tabular}{|r||r|r|r|r|r||r|r|r|}
        \hline
                        & $\grad$ ref  & $\grad$ est  & $\grad$ ratio       & $\grad$ est  & $\grad$ ratio  \\
        \hline
        $\calT_{C,5}$   & 0.317        & 4.317        & 13.581              & 3.246        & 10.214         \\
        \hline
        $\calT_{C,K}$   & 0.317        & 3.571        &  11.23              & 11.034       & 34.722         \\
        \hline
        $\calT_{B,5}$   & 1.022        & 7.698        & 7.5285              & 25.972       & 25.397         \\
        \hline
        $\calT_{B,K}$   & 1.022        & 10.106       & 9.8824              & 53.763       & 52.573         \\
        \hline
        $\calT_{F}$     & 0.711        & 10.622       & 14.927              &  268.071     & 377.033        \\ 
        \hline
    \end{tabular} 
    \caption{
    Estimates for $L^2$ Poincar\'e--Friedrichs constants of the gradient over various triangulated 3D domains.
    Reference values for the gradient (2nd column) computed with finite element methods together with estimates and ratios: 
    Theorem~\ref{theorem:poincarefriedrichsestimate:grad} (3rd and 4th column), and using Theorem~\ref{theorem:poincarefriedrichsestimate:exterior} with $k=0$ (5th and 6th column).
    }\label{table:estimates3D:grad}
\end{table}

\begin{table}[t]  
    \color{red}
    \centering
    \begin{tabular}{|r||r|r|r||r|r|r|}
        \hline
                        & $\curl$ ref  & $\curl$ est & $\curl$ ratio          & $\divergence$ ref & $\divergence$ est & $\divergence$ ratio \\ 
        \hline
        $\calT_{C,5}$   & 0.225        & 141.148     & 627.310506212          & 0.183             & 3.391             & 18.453          \\
        \hline
        $\calT_{C,K}$   & 0.225        & 12.157      & 54.0308334194          & 0.183             & 25.899            & 140.920         \\
        \hline
        $\calT_{B,5}$   & 0.331        & 113.084     & 341.056871148          & 0.233             & 152.886           & 655.993         \\
        \hline
        $\calT_{B,K}$   & 0.331        & 162.687     & 490.655711308          & 0.233             & 512.273           & 2198.026        \\
        \hline
        $\calT_{F}$     & 0.554        & 25752.342   & 46403.3023359          & 0.310             & 8958.467          & 28835.266       \\ 
        \hline
    \end{tabular}
    \caption{
    Estimates for $L^2$ Poincar\'e--Friedrichs constants over various triangulated 3D domains.
    Reference values for the curl and divergence (2nd and 5th column) computed with finite element methods together with estimates and ratios
    that rely on Theorem~\ref{theorem:poincarefriedrichsestimate:exterior} with $k=0$ (3rd and 4th column) and with $k=1$ (5th and 6th column).
    Note that the divergence constant can always be estimated using Lemma~\ref{lemma:mixedbconsimplex}.
    }\label{table:estimates3D:curldiv}
\end{table}

@@

The most important contribution of this manuscript is the computation of upper bounds of Poincar\'e--Friedrichs constants for the curl and divergence operators over local patches in low dimensions (i.e., \ $n=2$ or $n=3$). 
However, our upper bounds are hardly the last word on estimating the Poincar\'e--Friedrichs constants over local patches (stars). There are several avenues for further research and improvement, both in the analytical tools and the implementations.

We use local Poincar\'e--Friedrichs inequalities over single simplices, subject to boundary conditions along some faces. 
The estimates would improve considerably from sharper bounds on the local Poincar\'e constants. 
However, not many specific results seem to be available for the various special cases. 
The gradient Poincar\'e--Friedrichs constant already dominates the Poincar\'e--Friedrichs constants of the $\Lebesgue^2$ de~Rham complex without boundary conditions (or with full boundary conditions) over convex domains~\cite{guerini2004eigenvalue,licht2024geometry}. 
We believe that this generalizes to the entire range of Lebesgue exponents $1 \leq p \leq \infty$
Such estimates would likely improve on the Poincar\'e--Friedrichs constants derived via the regularized Poincar\'e and Bogovski\u{\i} operators. 
As mentioned in the manuscript, the Poincar\'e constant over triangles admits a sharper upper bound than for general convex domains. We conjecture that tetrahedra permit a similar improvement.
